Hydras \& Co.

### 2022-03-11 doc/gaia-chapter.tex
minor corrections

\chapter{Gaia and the hydras (draft)}
\index{coq}{Plug-ins!Gaia}
\label{gaia-chapter}

@@

The modules are located in {\texttt{theories/gaia/*.v}}.
The main entry point is
\href{../theories/html/gaia_hydras.T1Bridge.html}{gaia\_hydras.T1Bridge}, which requires both Gaia's \texttt{ssete9} and a few modules of \texttt{theories/ordinals/Epsilon0}.
Other modules are dedicated to the adaptation of several notions of \HydrasLib to \mathcomp's and \gaia's vocabulary and structures.
By default, we give priority to \gaia's notation and vocabulary.

@@

The function \texttt{g2h} is also used to provide a ``pretty'' printing of Cantor normal forms (please see Sect.~\vref{sect:ppT1}).

@@

For sake of compatibility, we add a clone of \texttt{hydra-battles}' type \texttt{E0} defined in \href{../theories/html/hydras.Epsilon0.E0.html}{Epsilon0.E0}.

@@

\inputsnippets{GCanon/gcanonLt}
\inputsnippets{GCanon/glimitCanonSNotZero}
\inputsnippets{GCanon/gcanonLimitMono}
\inputsnippets{GCanon/glimitCanonSNotZero}

@@

\begin{todo}
  Give equations for \texttt{F\_} (corresponding to the equation
  in \HydrasLib.
\end{todo}

>>>>

\chapter{Gaia and the hydra (draft)}
\index{coq}{Plug-ins!Gaia}
\label{gaia-chapter}

@@

The modules are named {\texttt{theories/gaia/*.v}} and coqdocumented in {\texttt{theories/html/gaia\_hydras.*.html}}
The main entry point is
\href{../theories/html/gaia_hydras.T1Bridge.html}{gaia\_hydras.T1Bridge}, which requires both Gaia's \texttt{ssete9} and a few modules of \texttt{theories/ordinals/Epsilon0}.
Other modules are dedicated to the adaptation of several notions of \HydrasLib to \mathcomp's and \gaia's vocabulary and structures.
By default, we give priority to \gaia's notation and vocabulary.

@@

The following function provides us with a more readable  printing of Cantor normal forms (please see Sect.~\vref{sect:ppT1}).

@@

For compatibility's sake, we add a clone of \texttt{hydra-battles}' type \texttt{E0} defined in \href{../theories/html/hydras.Epsilon0.E0.html}{Epsilon0.E0}.

@@

\inputsnippets{GCanon/gcanonLt}
\inputsnippets{GCanon/gcanonLimitMono}
\inputsnippets{GCanon/glimitCanonSNotZero}

@@

\begin{todo}
  Give equations for \texttt{F\_} (corresponding to the equation
  in \HydrasLib).
\end{todo}
